---
title: "ESM 206 Lab 8"
author: "Tommy King"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(modelsummary)
library(corrplot) 
library(broom)
library(here)
library(janitor)
```

```{r}
homes <- read_csv(here("slo_homes.csv")) %>% 
  clean_names()
```

### Create a subset  (called homes_subset) that only contains observations where the city is: 
- San Luis Obispo
- Atascadero
- Arroyo Grande
- Santa Maria- Orcutt

```{r}
homes_subset <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r}
homes_table <- homes_subset %>% 
  group_by(city, status) %>% 
  
  summarize(mean_price = mean(price), 
         sd_price = sd(price)) 

homes_table
```
 
 Task: Explore the relationship between square footage and home price. 
```{r}
ggplot(data = homes_subset, aes(x = sq_ft, y = price)) +
  geom_point(aes(color=city)) + 
  facet_wrap(~ city) +
  geom_smooth(method = "lm")
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price. 

Create 2 different permutations of this model. 
1. Price ~ city, bedrooms, bathrooms, sq_ft, status (lm1)
2. Price ~ city, sq_ft, status (lm2)
3. Try another one. (lm3)

```{r}
lm1 <- lm(price ~ city + bedrooms + bathrooms + sq_ft + status, data = homes_subset) 

tidy(lm1)
glance(lm1)

lm2 <- lm(price ~ city + sq_ft + status, data = homes_subset)

tidy(lm2)
glance(lm2)

# If i wanted San Luis Obispo to be the reference level: 
# Use fct_relevel() to specify a new reference level

#new_homes_subset <- homes_subset %>% 
#  mutate(city = fct_relevel(city, "San Luis Obispo"))



```

### Explore correlations betwwen quanitative variables 

Task: Make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through sq_ft. 

```{r}
homes_quant <- homes_subset %>% 
  select(price: sq_ft)

# use cor() function to view colinearity between the variables.
homes_cor <- cor(homes_quant)
# use corrplot() to visualize collinearity.
corrplot(homes_cor)
```


### COmpare AIC Values 
```{r}
AIC(lm1)
AIC(lm2)
# Smaller AIC value is better. 
# in literature, include all models so that readers can interpret on their own.
```
### Use modelsummary() to return multiple model outputs
```{r}
modelsummary(list(lm1, lm2))
# gives us information to compare different models directly.
```

### Check out the diganostic plots for lm1
```{r}
plot(lm1)
```
### Use broom::augment() to return the predictions for existing observations
```{r}
home_predictions <- augment(lm1)

# Make a histogram of the residuals from this model (lm1)

ggplot(data = home_predictions, aes(x = .resid)) + 
  geom_histogram()
# look for normal distribution of residuals.

```

# BRANCH TEST HOLLA
